A Graph Theory Based Approach to MDAO Problem Formulation

### 2013-04-19 graph_syntax.tex
updated per brian's suggestions

\subsection{Node and Edge Types}
  \label{ss:types}
  We now define different types of nodes and edges with specific properties to compose graphs used to represent an MDAO problem. 
  There are three node types:  
  \begin{description}
  \item[variable: ] represents scalar or array data
  \item[model:] responsible for mapping inputs to outputs
  \item[driver:] control logic capable of managing iteration
  \end{description}

@@

  \begin{description}
  \item[connection edge:] Exchange of information between two nodes. These edges 
  can either be fixed (can not be removed from graph) or free (can be removed). ((this needs to be modified, as analysis blocks cannot be altered but they can be removed as a group))
  \item [implicit edge:] Implicit passing of information from a driver node to a 
    variable node. A single variable node can have many incomming implicit edges. These edges are 
    free and can be added or removed from the graph. 
  \end{description}

@@

  In Alexandrov and Lewis's REMS syntax only two node types were present, variable 
  and function, and only one edge type\cite{alexandrov2004}. We've chosen to rename the ``function'' node 
  type to ``model'' to be more consistent with modern MDAO frameworks. The present work 
  adds two more node types and one more edge type to the syntax to allow descriptive
  graphs for all three phases of the design process.

\subsection{Rules for Nodes and Edges}
  \label{ss:rules}
  There are specific rules for the usage of these nodes and edges.
  The driver node and the implicit edge are only allowed to be present in PSGs. All 
  other node and edge types can be present in any of the three graphs, subject to these restrictions: 
  \begin{enumerate}
  \item A model node can only have one edge directed to or from another model node.
  \item A model node can only have fixed connection edges directed in or out.
  \item A model node must have at least one edge directed in and at least one edge 
    directed out.
  \item If a variable node has an outgoing edge to a model node then it may not have 
    any other outgoing edges.
  \end{enumerate}

\subsection{indegree and outdegree}
  \label{s:indegree-outdegree}
  The \emph{indegree} of a node is the number of connection edges directed in and 
  is denoted as $\txt{deg}^-(v)$, and the \emph{outdegree} 
  is the number of connection edges directed out and it is denoted as $\txt{deg}^+(v)$.
  The degree of a given node is only a function of the connection edges 
  attached to it. The number of implicit edges is not relevant since any number 
  of drivers could be involved, at different parts of an solution process. For 
  example in a sequential optimization where a global optimizer is first applied
  and a gradient based one is applied second, design variables would have incomming 
  implicit edges from both optimizers but this would not affect the indegree of those
  variable nodes. 
  ((DP:I started to remove any reference to the edge type in these definitions but then saw that you needed it. The reason I did that was because indegree and outdegree are basic graph theory terms. What if the reference to implicit edges is handled with the upper indegree limit, i.e. after the FPG is obtained the upper indegree limit for the design variable nodes is relaxed (increased) so that it isn't a problem what is or isn't counted?))

@@

\subsection{Design Variables}
((DP:I'm thinking we might also need the upper indegree limit to be zero as well, because setting only the lower indegree limit makes the node a design variable if it didn't have any incoming edges. It's seems possible that in the MCG a node has incoming edges but the user wants it to be a design variable. I can make the change if you agree.))
For the Sellar problem, there are three design variables, $x_1^*$, $z_1^*$, and $z_2^*$. In Fig. 
\ref{f:sellar_graph_full}, these are the only three holes (nodes without out 
incomming edges) in the graph.

@@

So a design variable is defined as any variable node with $\txt{deg}_l^-(v)=0$. 
This, by definition, means that design variables are not holes in the graph, since 
they have not violated their lower indegree limit. Regardless, 
when working with a MCG or FPG, only connection edges are allowed, so a design 
variable in either graph will be a variable with no incomming edges edges. For a valid PSG 
any design variable node would have at least one, but possibly multiple, incomming 
implicit edges from one or more driver nodes.

@@

  Coupling exists in a design problem when a set of two or more analyses each depend on the
  others outputs. In the Sellar problem from Eqn \ref{eqn:simple_fpf} the two 
  coupling constraints, $G_1$ and $G_2$ provide a reciprical dependence between 
  $D_1$ and $D_2$. In a graph, these constraints show up as connection edges between 
  the outputs of each analysis block. The relevant connection edges are highlighted in 
  Fig. \ref{f:coupling}, where they form a cycle. Cycles in a graph are the characteristic 
  structure that represents coupling.

>>>>

\subsection{Node and Edge Types}
  \label{ss:types}
  We now define different types of nodes and edges with specific properties to compose graphs used to represent an MDAO problem. 
  There are three node types:  
  \begin{description}
    \item[variable:] represents scalar or array data
    \item[model:] responsible for mapping inputs to outputs
    \item[driver:] control logic capable of managing iteration
  \end{description}

@@

  \begin{description}
  \item[connection edge:] Exchange of information between two nodes. These edges 
  can either be fixed (can not be removed from graph) or free (can be removed). 
  \item [driven edge:] Passing of information from a driver node to a 
    variable node. A single variable node can have many incomming driven edges. These edges are 
    free and can be added or removed from the graph. 
  \end{description}

@@

  In Alexandrov and Lewis's REMS syntax only two node types were present, variable 
  and function, and only one edge type\cite{alexandrov2004}. We've chosen to rename the ``function'' node 
  type to ``model'' to be more consistent with modern MDAO frameworks. The present work 
  adds one more node types and one more edge type to the syntax to allow descriptive
  graphs for all three phases of the design process. In addition, we introduce the 
  concept of fixed vs. free connection edges to represent the
  static relationship between variable and model nodes from a single analysis, 
  vs the flexible relationship between variables from different analyses.

\subsection{Rules for Nodes and Edges}
  \label{ss:rules}
  There are specific rules for the usage of these nodes and edges.
  The driver node and the driven edge are only allowed to be present in PSGs. All 
  other node and edge types can be present in any of the three graphs, subject to these restrictions: 
  \begin{enumerate}
  \item A model node can only have one edge directed to or from another model node.
  \item A model node can only have fixed connection edges directed in or out.
  \item A model node must have at least one edge directed in and at least one edge 
    directed out.
  \item If a variable node has an outgoing edge to a model node then it may not have 
    any other outgoing edges.
  \end{enumerate}

\subsection{indegree and outdegree}
  \label{s:indegree-outdegree}
  The \emph{indegree} of a node is the number of connection edges directed in and 
  is denoted as $\txt{deg}^-(v)$, and the \emph{outdegree} 
  is the number of connection edges directed out and it is denoted as $\txt{deg}^+(v)$.
  The degree of a given node is only a function of the connection edges 
  attached to it. The number of driven edges is not relevant since any number 
  of drivers could be involved, at different parts of an solution process. For 
  example in a sequential optimization where a global optimizer is first applied
  and a gradient based one is applied second, design variables would have incomming 
  driven edges from both optimizers but this would not affect the indegree of those
  variable nodes.

@@

\subsection{Design Variables}
For the Sellar problem, there are three design variables, $x_1^*$, $z_1^*$, and $z_2^*$. In Fig. 
\ref{f:sellar_graph_full}, these are the only three holes (nodes without out 
incomming edges) in the graph.

@@

So a design variable is defined as any variable node with $\txt{deg}_l^-(v)=0$. 
This, by definition, means that design variables are not holes in the graph, since 
they have not violated their lower indegree limit. Regardless, 
when working with a MCG or FPG, only connection edges are allowed, so a design 
variable in either graph will be a variable with no incomming edges edges. For a valid PSG 
any design variable node would have at least one, but possibly multiple, incomming 
driven edges from one or more driver nodes.

@@

  Coupling exists in a design problem when a set of two or more analyses each depend on the
  others outputs. In the Sellar problem from Eqn \ref{eqn:simple_fpf} the two 
  coupling constraints, $H_1$ and $H_2$ provide a reciprical dependence between 
  $D_1$ and $D_2$. In a graph, these constraints show up as connection edges between 
  the outputs of each analysis block. The relevant connection edges are highlighted in 
  Fig. \ref{f:coupling}, where they form a cycle. Cycles of connection edges are the characteristic 
  structure that represents coupling.

### 2013-04-19 intro.tex
updated per brian's suggestions

\section{Specific vs Fundamental Problem Formulation }
	\label{s:specific vs fundamental}
    The Fundamental Problem Formulation (FPF) for any given problem will be constant regardless 
    of which MDAO framework, optimization algorithm, iterative solver, or solution strategy
    is used to solve the problem. However, it is possible to formulate a problem
    with an assumed execution ordering that implies a solution strategy. 
    For example, consider the Sellar test problem \cite{AIAA:sellar}:

    \begin{align}
        given & \ \ y_1 = D_1(x_1,y_2,z_1,z_2) \notag
        \\      & \ \ y_2^t = D_2(y_1,z_1,z_2) \notag
        \\min. &\ \ F(x_1,y_1,y_2,z_2) \notag
        \\w.r.t. & \ \ x_1,y_1,y_2,z_1,z_2 \notag
        \\s.t. & \ \ G(y_2,y_2^t) = 0
        \label{eqn:simple}
    \end{align}

    $D_1$ and $D_2$ represent analysis tools, and $F$ and $G$ are the objective 
    and constraint functions respectively. Equation \ref{eqn:simple} makes an 
    inherent assumption about the solution strategy for the problem. Analysis 
    $D_1$ outputs $y_1$, which is an input to $D_2$. Hence, $D_1$ should be run 
    before $D_2$ with with $y_2$ being iterated on to convergence with $y_2^t$. 
    However, a slightly different formulation is equally valid and still 
    represents the exact same problem:

    \begin{align}
        given & \ \ y_2 = D_2(y_1,z_1,z_2) \notag
        \\      & \ \ y_1^t = D_1(x_1,y_2,z_1,z_2) \notag
        \\min. &\ \ F(x_1,y_1,y_2,z_2) \notag
        \\w.r.t. & \ \ x_1,y_1,y_2,z_1,z_2 \notag
        \\s.t. & \ \ G(y_1,y_1^t) = 0
        \label{eqn:simple2}
    \end{align}

    Equation \ref{eqn:simple2} differs only slightly from Eq. \ref{eqn:simple}. 
    $D_1$ is now dependent on the output of $D_2$, and $y_1$ will be iterated on to 
    convergence with $y_1^t$. Now the problem can be solved by running $D_2$ first 
    and then $D_1$. Since the formulations in Eqs. \ref{eqn:simple} and 
    \ref{eqn:simple2} both describe the same problem then neither can be the
    FPF. They are both specific versions of a more fundamental description of 
    the problem that is common between them. We present the fundamental 
    formulation as follows:

    \begin{align}
        given & \ \ D_1.y_1 = D_1(x_1,y_2,z_1,z_2) \notag
        \\      & \ \ D_2.y_2 = D_2(y_1,z_1,z_2) \notag
        \\min. &\ \ F(x_1,y_1,y_2,z_2) \notag
        \\w.r.t. & \ \ x_1,y_1,y_2,z_1,z_2 \notag
        \\s.t. & \ \ G_1(D_1.y_1,D_2.y_1) = 0 \notag
        \\     & \ \ G_2(D_1.y_2,D_2.y_2) = 0
        \label{eqn:simple_fpf}
    \end{align}

    The formulation in Eq. \ref{eqn:simple_fpf} differs from both Eq. \ref{eqn:simple} 
    and Eq. \ref{eqn:simple2} because it has two constraints which both must be 
    met. The presence of both of these constraints fully decouples the problem so that 
    either $D_1$ or $D_2$ could be run first or both could be run simultaneously. 
    Alexandrov and Lewis, in their work with REMS, assert that fully decoupling 
    the analyses is key to achieving reconfigurability in the problem 
    formulation\cite{alexandrov2004}. The key feature they identify to allow this decoupling 
    is the creation of separate variables for each analysis so that a variable 
    is identified by its analysis and it's name. For example, in Eqn. \ref{eqn:simple}
    there is only one $y_1$ variable vs Eqn. \ref{eqn:simple_fpf} where 
    there are two ($D_1.y_1$ vs $D_2.y_1$).

@@

    Steward's Design Structure Matrix (DSM) is a square adjacency matrix which captures the relationship between analysis tools where off 
    diagonal elements of the matrix indicate coupling\cite{Steward1981}. Since a DSM describes a square adjacency matrix, 
    it can be represented in an equivalent directed graph where nodes represent analysis tools and 
    edges represent information dependence between those tools. The ordering of elements in a DSM can be used to indicate 
    execution order.  For more complex problems, choosing the proper order to run analysis tools is a non-trival task. 
    Rogers et. al developed DeMAID to manipulate a DSM to find an ordering for analysis tools that 
    reduces the cost of solving highly coupled systems\cite{rogers1996,rogers1996demaid}. This re-ordering is done through 
    row operations on the DSM matrix and yields multiple specific problem 
    formulations which all solve the same FPF. In other words, manipulation of the DSM does not fundamentally alter
    the problem formulation, which makes DSM an excellent foundation for specifying the FPF itself.

    Despite it's attractive properties, a DSM by itself is insufficient to describe complete problem formulations. 
    Traditional DSM only captures information about data dependency between analyses. 
    Objective and constraint information is missing from the description of the problem. 
    An alternative matrix-based syntax, called a Functional Dependency Table (FDT), was proposed by Wagner and Papalambros. 
    FDT represents the relationship between functions, including objectives and constraints, and specific variables that affect 
    them\cite{Wagner1993}. Similar to DSM, FDT also describes an adjacency matrix of a graph. Unlike the DSM graph, 
    however, the graph is undirected and nodes can represent analysis tools, objectives, 
    or constraints. Edges between nodes represent a dependence on the same 
    variable. Michelena and Papalambros made use of the FDT to solve a graph partitioning problem that yielded 
    more efficient optimization problem decompositions\cite{Michelena1997}. While FDT succeeds at capturing the 
    information about objectives and constraints, it can not capture the coupled data dependency that DSM captures. For instance, 
    we know from the FPF in Eq. \ref{eqn:simple_fpf} that the objective, $f$, is dependent on the 
    output, $m$, of analysis $A$. You could not determine that from the FDT in Fig. \ref{fig:FDT_simple} alone. This missing 
    information means that, while FDT is very useful for partitioning problems, it is also not sufficient to contain a 
    complete problem formulation.

@@

    Alexandrov and Lewis introduced a graph based syntax called REMS which 
    incorporates objectives and constraints into a graph, effectively combining 
    FDT and DSM\cite{alexandrov2004}. REMS retains the square adjacency 
    matrix form from DSM, but by adding in the new elements it partially 
    combined a traditional DSM with an FDT. This allows REMS to represent data 
    dependency between multiple analysis tools as well as between analysis tools and
    objective/constraint functions. One significant conclusion from REMS is 
    the need for variables that are local to discipline analyses. This allows 
    all information exchange to be stated as equality constraints, which become 
    edges in the graph. Additionaly, REMS address the need to be able to 
    transition between multiple solution strategies while keeping a constant 
    graph representation of the fundamental problem formulation. REMS only provides
    syntax for variables and functions, but does not provide for inclusion 
    of solvers or optimizers in the graph.

@@

    Although XDSM captures part of the functional aspects of FDT, it leaves out the variables themselves.  
    As a result, all variable information is aggregated 
    so that for the problem from Eq. \ref{eqn:simple_fpf} you can say that $A$ 
    depends on $B$ or vice versa, but you can't identify which 
    individual variables are interacting in the dependency cycle. 
    Without the detailed variable information, you can't construct the compatibility 
    constraints necessary to implement the problem. Additionally, XDSM 
    requires the use of solver and optimizer blocks to represent 
    the relationship between design variables and objectives/constraints. 
    By introducing solver or optimizer blocks XDSM automatically provides
    some kind of solution strategy. The XDSM for Eq. \ref{eqn:simple} is 
    given in Figure \ref{fig:XDSM_simple}. This diagram is shown with an 
    assumed gauss-siedel iteration scheme and a MDF solution architecture. 
    Hence XDSM is too specific for use with a fundamental problem formulation.

    Of all the methods, REMS comes the closest to fully describing a problem formulation,
    but lacks the ability to represent optimziers and solvers in more specific problem 
    formulations. While XDSM does include optimizers and constraints, it relies on 
    their presence and can't be used for a more fundamental problem statement. 
    We propose a new graph syntax that combines the key features of REMS and XDSM
    and provides new language to enable more complete description of MDAO problems.

>>>>

\section{Specific vs Fundamental Problem Formulation }
	\label{s:specific vs fundamental}
    The Fundamental Problem Formulation (FPF) for any given problem will be constant regardless 
    of which MDAO framework, optimization algorithm, iterative solver, or execution sequence
    is used to solve the problem. However, it is very easy to formulate a problem without 
    any reference to a specific solution strategy, but still impose a a specific execution sequence.
    For example, consider the Sellar test problem \cite{AIAA:sellar}:

    \begin{align}
        given & \ \ y_1 = D_1(x_1,\hat{y_2},z_1,z_2) \notag
        \\      & \ \ y_2 = D_2(y_1,z_1,z_2) \notag
        \\min. &\ \ F(x_1,y_1,y_2,z_2) \notag
        \\w.r.t. & \ \ x_1,y_1,\hat{y_2},z_1,z_2 \notag
        \\s.t. & \ \ H(y_2,\hat{y_2}) = 0 \notag 
        \\     & \ \ G_1(y_1) \geq 0 \notag
        \\     & \ \ G_2(y_2) \geq 0
        \label{eqn:simple}
    \end{align}

    $D_1$ and $D_2$ represent analysis tools, $F$, $G_1$, and $G_2$ are the objective 
    and constraint functions respectively, and $H$ is the coupling constraint. 
    Equation \ref{eqn:simple} makes an inherent assumption about the execution 
    order for the problem. Analysis $D_1$ outputs $y_1$, which is an input to $D_2$. 
    Hence, $D_1$ should be run before $D_2$ with with $y_2$ being iterated on 
    to convergence with $\hat{y_2}$. However, a slightly different formulation 
    is equally valid and still represents the exact same problem:

    \begin{align}
        given & \ \ y_2 = D_2(\hat{y_1},z_1,z_2) \notag
        \\      & \ \ y_1 = D_1(x_1,y_2,z_1,z_2) \notag
        \\min. &\ \ F(x_1,y_1,y_2,z_2) \notag
        \\w.r.t. & \ \ x_1,\hat{y_1},y_2,z_1,z_2 \notag
        \\s.t. & \ \ H(y_1,\hat{y_1}) = 0 \notag 
        \\     & \ \ G_1(y_1) \geq 0 \notag
        \\     & \ \ G_2(y_2) \geq 0
        \label{eqn:simple2}
    \end{align}

    Equation \ref{eqn:simple2} differs only slightly from Eq. \ref{eqn:simple}. 
    Notice that the formulation from Eq. \ref{eqn:simple} includes 
    $\hat{y_2}$, while Eq. \ref{eqn:simple2} includes $\hat{y_2}$. The result is that
    $D_1$ is now dependent on the output of $D_2$, and $y_1$ will be iterated on to 
    convergence with $\hat{y_1}$. Now the problem has to be solved by running $D_2$ first 
    and then $D_1$. Since the formulations in Eqs. \ref{eqn:simple} and 
    \ref{eqn:simple2} both describe the same problem then neither can be the
    FPF. They are both specific versions of a more fundamental description of 
    the problem that is common between them. We present the fundamental 
    formulation as follows:

    \begin{align}
        given & \ \ y_1 = D_1(x_1,\hat{y_2},z_1,z_2) \notag
        \\      & \ \ y_2 = D_2(\hat{y_1},z_1,z_2) \notag
        \\min. &\ \ F(x_1,y_1,y_2,z_2) \notag
        \\w.r.t. & \ \ x_1,\hat{y_1},\hat{y_2},z_1,z_2 \notag
        \\s.t. & \ \ H_1(y_1,\hat{y_1}) = 0 \notag
        \\     & \ \ H_2(y_2,\hat{y_2}) = 0 \notag 
        \\     & \ \ G_1(y_1) \geq 0 \notag
        \\     & \ \ G_2(y_2) \geq 0
        \label{eqn:simple_fpf}
    \end{align}

    The formulation in Eq. \ref{eqn:simple_fpf} differs from both Eq. \ref{eqn:simple} 
    and Eq. \ref{eqn:simple2} because it has two coupling constraints which both must be 
    met. The result is that Eq. \ref{eqn:simple_fpf} required the presence of both 
    $\hat{y_1}$ and $\hat{y_2}$, which means that $D_1$ and $D_2$ each now operate with 
    their own local copies of the coupling variables. This fully decouples the problem so that 
    either $D_1$ or $D_2$ could be run first or both could be run simultaneously. 
    Alexandrov and Lewis, in their work with REMS, assert that fully decoupling 
    the analyses is key to achieving reconfigurability in the problem 
    formulation\cite{alexandrov2004}. The key feature they identify to allow this decoupling 
    is the creation of independent variables for each analysis. Tosserams et. al. 
    in their development of the $\psi$ language for heirarchical problem composition
    make the same requirement that all analyses get their own local copies of 
    variables in order to use them as the fundamental building blocks for 
    problems\cite{tosserams2010specification}. Martins and Hwang derive the same requirement,
    from a different perspective, in their work on computing analytic derivatives 
    for MDAO problems\cite{Martins2012}. They determined that local copies of all variables 
    allows for derivation of all relevant methods for calculating analytic derivatives 
    from the basic chain rule.

@@

    Steward's Design Structure Matrix (DSM) is a square adjacency matrix which captures the relationship between analysis tools where off 
    diagonal elements of the matrix indicate coupling\cite{Steward1981}. Since a DSM describes a square adjacency matrix, 
    it can be represented in an equivalent directed graph where nodes represent analysis tools and 
    edges represent information dependence between those tools. The ordering of elements in a DSM can be used to indicate 
    execution order.  For more complex problems, choosing the proper order to run analysis tools is a non-trival task. 
    Rogers et. al developed DeMAID to manipulate a DSM to find an ordering for analysis tools that 
    reduces the cost of solving highly coupled systems\cite{rogers1996,rogers1996demaid}. This re-ordering is done through 
    row operations on the DSM matrix and yields multiple specific problem 
    formulations which all solve the same FPF.

    Despite it's attractive properties, a DSM by itself is insufficient to describe complete problem formulations. 
    Traditional DSM only captures information about data dependency between analyses. 
    Objective and constraint information is missing from the description of the problem. 
    An alternative matrix-based syntax, called a Functional Dependency Table (FDT), was proposed by Wagner and Papalambros. 
    FDT represents the relationship between functions, including objectives and constraints, and specific variables that affect 
    them\cite{Wagner1993}. Similar to DSM, FDT also describes an adjacency matrix of a graph. Unlike the DSM graph, 
    however, the graph is undirected and nodes can represent analysis tools, objectives, 
    or constraints. Edges between nodes represent a dependence on the same 
    variable. Michelena and Papalambros made use of the FDT to solve a graph partitioning problem that yielded 
    more efficient optimization problem decompositions\cite{Michelena1997}. While FDT succeeds at capturing the 
    information about objectives and constraints, it can not capture the coupled data dependency that DSM captures. For instance, 
    we know from the FPF in Eq. \ref{eqn:simple_fpf} that the objective, $f$, is dependent on the 
    output, $m$, of analysis $A$. The dependence of $m$ on $A$ is now captured 
    in FDT in Fig. \ref{fig:FDT_simple} alone. This missing information means 
    that, while FDT is very useful for partitioning problems, it is also not 
    sufficient to contain a complete problem formulation.

@@

    Alexandrov and Lewis introduced a graph based syntax called REMS which 
    incorporates objectives and constraints into a graph, effectively combining 
    FDT and DSM\cite{alexandrov2004}. REMS retains the square adjacency 
    matrix form from DSM, but by adding in the new elements it partially 
    combined a traditional DSM with an FDT. This allows REMS to represent data 
    dependency between multiple analysis tools as well as between analysis tools and
    objective/constraint functions. Additionaly, REMS address the need to be able to 
    transition between multiple solution strategies while keeping a constant 
    graph representation of the fundamental problem formulation. REMS only provides
    syntax for variables and functions, but does not provide for inclusion 
    of solvers or optimizers in the graph.

@@

    Although XDSM captures part of the functional aspects of FDT, it 
    requires the use of solver and optimizer blocks to represent 
    the relationship between design variables and objectives/constraints. 
    By introducing solver or optimizer blocks XDSM automatically provides
    some kind of solution strategy. The XDSM for Eq. \ref{eqn:simple} is 
    given in Figure \ref{fig:XDSM_simple}. This diagram is shown with an 
    assumed gauss-siedel iteration scheme and a MDF solution architecture. 
    Hence XDSM is too specific for use with a fundamental problem formulation.

    Of all the methods, REMS comes the closest to fully describing a fundamental 
    problem formulation, but lacks the ability to represent optimziers and 
    solvers in more specific problem formulations. While XDSM does include 
    optimizers and constraints, it relies on their presence and can't be used 
    for a more fundamental problem statement. We propose a new graph syntax that 
    combines the key features of REMS and XDSM while retaining the flexiblity to 
    represent a fundamental problem formulation free of solution specific information.
